
\documentclass{article} % For LaTeX2e
\usepackage{iclr2026_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

% \usepackage{hyperref}
\usepackage[colorlinks=true, linkcolor=black, citecolor=green, urlcolor=blue]{hyperref}
\usepackage{url}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{pifont}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{svg}
\usepackage[para]{footmisc}
\usepackage{amssymb}


\title{Primary-Fine Decoupling for Action Generation in Robotic Imitation}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

% \author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
% about author (webpage, alternative address)---\emph{not} for acknowledging
% funding agencies.  Funding acknowledgements go at the end of the paper.} \\
% Department of Computer Science\\
% Cranberry-Lemon University\\
% Pittsburgh, PA 15213, USA \\
% \texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
% \And
% Ji Q. Ren \& Yevgeny LeNet \\
% Department of Computational Neuroscience \\
% University of the Witwatersrand \\
% Joburg, South Africa \\
% \texttt{\{robot,net\}@wits.ac.za} \\
% \AND
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email}
% }

\author{
  % 作者姓名部分
  Xiaohan Lei$^1$, 
  Min Wang$^{2,}$\thanks{Corresponding authors: Min Wang (wangmin@iai.ustc.edu.cn) and Wengang Zhou (zhwg@ustc.edu.cn).} , 
  Wengang Zhou$^{1, 2, \dagger}$, 
  Xingyu Lu$^1$, 
  Houqiang Li$^{1, 2}$ \\
  \\ % 空一行，区分名字和机构
  $^1$MoE Key Laboratory of Brain-inspired Intelligent Perception and Cognition, \\
  University of Science and Technology of China \\
  $^2$Institute of Artificial Intelligence, Hefei Comprehensive National Science Center \\
  \\ % 空一行，区分机构和邮箱
  \texttt{\{leixh, luxingyu010\}@mail.ustc.edu.cn} \\
  \texttt{wangmin@iai.ustc.edu.cn, \{zhwg, lihq\}@ustc.edu.cn}\\
  \\
  \normalfont Project Page: \quad \url{https://xiaohanlei.github.io/projects/PF-DAG}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\definecolor{tablecolor}{HTML}{ccf2f5} 
\definecolor{tablecolor2}{HTML}{dcf5eb} 

\newcommand{\mymethod}{PF-DAG}
\newcommand{\tb}[1]{\textbf{#1}}
\newcommand{\yes}{\color{blue}{\ding{51}}}
\newcommand{\no}{\color{red}{\ding{55}}}
\newcommand{\sg}[1]{\text{sg}(#1)}
\newcommand{\dd}[2]{$#1\scriptstyle{\pm#2}$}
\newcommand{\ddbf}[2]{$\mathbf{#1\scriptstyle{\pm#2}}$}
\newcommand{\ddbfgreen}[2]{\cellcolor{tablecolor2}$\mathbf{#1\scriptstyle{\pm#2}}$}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle


% *****************TODO**********************
\begin{abstract}
Multi-modal distribution in robotic manipulation action sequences poses critical challenges for imitation learning. 
To this end, existing approaches often model the action space as either a discrete set of tokens or a continuous, latent-variable distribution.
However, both approaches present trade-offs: some methods discretize actions into tokens and therefore lose fine-grained action variations, while others generate continuous actions in a single stage tend to produce unstable mode transitions.
To address these limitations, we propose Primary-Fine Decoupling for Action Generation (\mymethod), a two-stage framework that decouples coarse action consistency from fine-grained variations. First, we compress action chunks into a small set of discrete modes, enabling a lightweight policy to select consistent coarse modes and avoid mode bouncing. Second, a mode conditioned MeanFlow policy is learned to generate high-fidelity continuous actions.
Theoretically, we prove \mymethod’s two-stage design achieves a strictly lower MSE bound than single-stage generative policies. 
Empirically, \mymethod{} outperforms state-of-the-art baselines across 56 tasks from Adroit, DexArt, and MetaWorld benchmarks. It further generalizes to real-world tactile dexterous manipulation tasks. Our work demonstrates that explicit mode-level decoupling enables both robust multi-modal modeling and reactive closed-loop control for robotic manipulation.
\end{abstract}

\input{sections/introduction}
\input{sections/related_work}
\input{sections/method}
\input{sections/exp}
\input{sections/conclusion}


\section{Acknowledgments}

This work was supported by the National Natural Science Foundation of China under Contract 62472141, the Natural Science Foundation of Anhui Province under Contract 2508085Y040, and the Youth Innovation Promotion Association CAS. It was also supported by the GPU cluster built by MCC Lab of Information Science and Technology Institution, USTC and the Supercomputing Center of USTC.


\bibliography{main}
\bibliographystyle{iclr2026_conference}

% \input{sections/appendix}


\end{document}
